---
title: "What made you happy today?"
output:
  html_document:
    df_print: paged
---

# Introduction

It has become increasingly important for us to know what makes us happy due to the fast-paced lifestyle nowadays.And aftering some analyse on the 100000 happy moments,I am going to tell a story about happpiness and show the base of my story.


## First step: importing and merging data

```{r warning=FALSE}
clean = read.csv("./data/cleaned_hm.csv",header = T)
demo = read.csv("./data/demographic.csv",header = T)
combine = merge (clean,demo,by="wid",all=F)
```

There are serval stages in our life: when we are juveniles, becoming adults,getting married, with baby born,we become parents and so on. We have different identites and thus duties in different stages, therefore, reasons that why we are happy may show up differently. However, there are still something always make us happy.

##Second step: spliting data


```{r warning=FALSE}
table(demo$country)
table(demo$gender)
table(demo$marital)
table(demo$parenthood)
```

Above are four differents ways to classify people we have recorded. On the first way, we found that most people in the data come from ths USA and IND, thus we need to split these two type of people out from the original data.

```{r warning=FALSE}
ll <- split(combine,combine$country)
USA <- ll$USA
IND <- ll$IND
```

Then, let us see the difference between these two types of people.

```{r warning=FALSE}
rate <- function(name){
  return(table(name)/length(name))
}
rate(USA$predicted_category)
rate(IND$predicted_category)
```

First of all, achivement and affection are two main reasons that make people happy for both of these countries. But,people from USA are more likely to be happy because of achievement compared to people from IND. USA is a developed country, and IND is a developing country, therefore, it is likely that better the economy, greater chance for people to chase their goal and enjoy it. What' more, people from USA enjoy more on exercise than IND people do, this makes sense because there are so many world-famous sports leage, such as NBA in USA. This also based on good economy. In a word, with the economy developed, people's happyiness foucus will transit from affection to achievement. My further anaylse would base on people from the USA.

## Third step: defining life's stage

The first stage is juvenile, which means age under 18. The following stage would be life before marry. We need to find out the average age that people from the data get married. Usually, male get married later than female do, and there are many other difference between male and female, thus, we need to seperate people according to their gender.

```{r warning=FALSE}
gender <- split(USA,USA$gender)
male <- gender$m
female <- gender$f
rate(male$predicted_category)
rate(female$predicted_category)
```

Clearly, female are much more likely to be happy due to affection than male do, this corresponds to the saying: male are rational and female are sensuous. This also could be explained on the foot of economy: male are richer than female on average.  Next, let us find out the averaged marry age for male and female.

```{r warning=FALSE}
table(male$marital)
library(ggplot2)
ggplot(male,aes(x=marital,y=as.numeric(age)))+geom_violin()+geom_boxplot(width=0.1)
ggplot(female,aes(x=marital,y=as.numeric(age)))+geom_violin()+geom_boxplot(width=0.1)
```

Most male are either married or single, thus only these two types of male need to be considered. For male, less than a quarter of single male are aged over 23, and age of married male clustering  on the same age. Therefore, it is reasonable to choose 23 to be the averaged married age for male. Using the same method, averaged married age for female would be 25.
When it comes to the third stage, when people become parents, we still use the way above to find out the age people start to become parents.

```{r warning=FALSE}
ggplot(male,aes(x=parenthood,y=as.numeric(age)))+geom_violin()+geom_boxplot(width=0.1)
ggplot(female,aes(x=parenthood,y=as.numeric(age)))+geom_violin()+geom_boxplot(width=0.1)
```

The age for both male and female to become parents are almost the same as that to ger married. Thus, we need to combine the second and the third stage together.
According to the USA law, both male and female are retire at the age of 65, thus, age over 65 would be the last stage. However, the third stage would last too long, so,dividing the third stage into two part: age before 40 and age after 40. There are totally 5 stages in the end.

### Male

```{r warning=FALSE}
mstage1 <- male$predicted_category[which(as.numeric(male$age)<18)]
mstage2 <- male$predicted_category[which(as.numeric(male$age)<24&as.numeric(male$age)>17)]
mstage3 <- male$predicted_category[which(as.numeric(male$age)<40&as.numeric(male$age)>23)]
mstage4 <- male$predicted_category[which(as.numeric(male$age)<65&as.numeric(male$age)>39)]
mstage5 <- male$predicted_category[which(as.numeric(male$age)>64)]
ms1 <- rate(mstage1)
ms2 <- rate(mstage2)
ms3 <- rate(mstage3)
ms4 <- rate(mstage4)
ms5 <- rate(mstage5)
stage <- c(1,2,3,4,5,1,2,3,4,5)
machievement <- c(ms1[1],ms2[1],ms3[1],ms4[1],ms5[1])
maffection <- c(ms1[2],ms2[2],ms3[2],ms4[2],ms4[2])
```



### Female

```{r warning=FALSE}
fstage1 <- female$predicted_category[which(as.numeric(male$age)<18)]
fstage2 <- female$predicted_category[which(as.numeric(male$age)<26&as.numeric(male$age)>17)]
fstage3 <- female$predicted_category[which(as.numeric(male$age)<40&as.numeric(male$age)>25)]
fstage4 <- female$predicted_category[which(as.numeric(male$age)<65&as.numeric(male$age)>39)]
fstage5 <- female$predicted_category[which(as.numeric(male$age)>64)]
fs1 <- rate(fstage1)
fs2 <- rate(fstage2)
fs3 <- rate(fstage3)
fs4 <- rate(fstage4)
fs5 <- rate(fstage5)
fachievement <- c(fs1[1],fs2[1],fs3[1],fs4[1],fs5[1])
faffection <- c(fs1[2],fs2[2],fs3[2],fs4[2],fs5[2])
sex=c(rep("m",5),rep("f",5))
```


## Step forth: Graphic analyse
```{r warning=FALSE}
mf <- data.frame(stage=stage,achievement=c(machievement,fachievement),affection=c(maffection,faf=faffection),gender=as.factor(sex))
p <- ggplot(mf)+geom_line(mapping = aes(x=stage,y=achievement,colour=gender))
print(p)
q <- ggplot(mf)+geom_line(mapping = aes(x=stage,y=affection,colour=gender))
print(q)
```
 
From plot 1, there are serval conclusions. First: male are more likely to be happy because of achievement than female do. Second: In general, with the aged increased, male become less likely to be pleased by achievement. Third, it is wired that female's interesting on achievement sharply decrease in the forth stage. This may happen because after marrage, female pay much more attention to the family than male do and have less time to achieve their goals, this may also explain why female become more enjoy on achievement after retirement.
When it comes to plot 2,both male female become more likely to be pleased by affection with the age increased in general, especially for men, the pace their interesting grows on affection is amazing. For female, they are less likely to be happy because of affection on their second stage.

## Step fifth: Conclusion

No matter where you come from, no matter you are male or female, and no matter how old you are, the main reasons why you would be happy are affection and achievement. Better economy leads to greater chance people to be pleased by achievement. On the early stage of our life, male are more enjoy chasing their goals and  less likely to be pleased by affection. But with age increased, this becomes totally different. Female always pay more focus on affection, and focus more and more with age increased. Their interesting on achievement change little through the life.

```{r warning=FALSE}
library(tm)
library(SnowballC)
library(tidytext)
library(wordcloud)
library(RColorBrewer)
library(RColorBrewer)
library(dplyr)
```

### Word Frequency

```{r warning=FALSE}
senselabel = read.csv("./data/senselabel.csv")
sen = senselabel %>% group_by(hmid) %>% summarise(sent = paste(lowercaseLemma, collapse = ' ')) %>% as.data.frame()
data = merge(clean, sen, by.x = "hmid", by.y = "hmid")
pre = split(data,data$predicted_category)
```

```{r warning=FALSE}
prepro = function(data) {
  corpus = VCorpus(VectorSource(data$sent))
  corpus = tm_map(corpus, removePunctuation)
  corpus = tm_map(corpus, removeWords, stopwords())
  ttt = TermDocumentMatrix(corpus)
  ttt.tidy = tidy(ttt)
  ttt.overall = summarise(group_by(ttt.tidy, term), sum(count))
  return(ttt.overall)
}
```

### Key words in achievement, from the plot we know that new thing, work and get something easily make people happy.

```{r warning=FALSE}
ttt.overall = prepro(pre$achievement)
wordcloud(ttt.overall$term, ttt.overall$`sum(count)`,
          scale=c(5,0.5), max.words=100,
          min.freq=1, random.order=FALSE,
          rot.per=0.3, use.r.layout=T,
          random.color=FALSE, colors=brewer.pal(9,"Blues"))
```

### As for affection, key words focous more on our families and friends.

```{r warning=FALSE}
ttt.overall = prepro(pre$affection)
wordcloud(ttt.overall$term, ttt.overall$`sum(count)`,
          scale=c(5,0.5), max.words=100,
          min.freq=1, random.order=FALSE,
          rot.per=0.3, use.r.layout=T, 
          random.color=FALSE, colors=brewer.pal(9,"Blues"))
```

```{r warning=FALSE}
ttt.overall = prepro(pre$exercise)
wordcloud(ttt.overall$term, ttt.overall$`sum(count)`,
          scale=c(5,0.5), max.words=100,
          min.freq=1, random.order=FALSE,
          rot.per=0.3, use.r.layout=T,
          random.color=FALSE, colors=brewer.pal(9,"Blues"))
```

### TF-IDF: Instead of counting the word frequencies directly, we can also caculate TF-IDF which is more represently for word importance. We can find a slightly difference of wordcloud using word frequence and TF-IDF.

```{r warning=FALSE}
corpus = VCorpus(VectorSource(pre))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, removeWords, stopwords())

```

```{r warning=FALSE}
dtm = DocumentTermMatrix(corpus,
                          control = list(weighting = function(x)
                                             weightTfIdf(x, 
                                                         normalize =FALSE),
                                         stopwords = TRUE))
ff.dtm = tidy(dtm)
ff.dtm$document[ff.dtm$document == 1] = "achievement"
ff.dtm$document[ff.dtm$document == 2] = "affection"
ff.dtm$document[ff.dtm$document == 3] = "bonding"
ff.dtm$document[ff.dtm$document == 4] = "enjoy_the_moment"
ff.dtm$document[ff.dtm$document == 5] = "exercise"
ff.dtm$document[ff.dtm$document == 6] = "leisure"
ff.dtm$document[ff.dtm$document == 7] = "nature"

```

```{r warning=FALSE}
emtions = c("achievement", "affection", "bonding", "enjoy_the_moment", "exercise", "leisure", "nature")
library(shiny)
shinyApp(
    ui = fluidPage(
      fluidRow(style = "padding-bottom: 20px;",
        column(4, selectInput('speech1', 'Emotion 1', emtions,
                              selected = emtions[1])),
        column(4, selectInput('speech2', 'Emotion 2', emtions,
                              selected = emtions[2])),
        column(4, sliderInput('nwords', 'Number of words', 3,
                               min = 20, max = 200, value=100, step = 20))
      ),
      fluidRow(
        plotOutput('wordclouds', height = "400px")
      )
    ),
    server = function(input, output, session) {
      # Combine the selected variables into a new data frame
      selectedData <- reactive({
        list(dtm.term1=ff.dtm$term[ff.dtm$document == input$speech1],
             dtm.count1=ff.dtm$count[ff.dtm$document == input$speech1],
             dtm.term2=ff.dtm$term[ff.dtm$document == input$speech2],
             dtm.count2=ff.dtm$count[ff.dtm$document == input$speech2])
      })
      output$wordclouds <- renderPlot(height = 400, {
        par(mfrow=c(1,2), mar = c(0, 0, 3, 0))
        wordcloud(selectedData()$dtm.term1, 
                  selectedData()$dtm.count1,
              scale = c(5,0.5),
              max.words=input$nwords, min.freq = 3,
              random.order=FALSE, rot.per=0.3,
              use.r.layout=FALSE, random.color=FALSE,
              colors=brewer.pal(9, "Blues"), 
            main=input$speech1)
        wordcloud(selectedData()$dtm.term2, 
                  selectedData()$dtm.count2,
              scale=c(5,0.5),
              max.words = input$nwords,
              min.freq = 3, random.order = FALSE,
              rot.per = 0.3, use.r.layout = FALSE,
              random.color = FALSE, 
              colors=brewer.pal(9, "Blues"), 
            main=input$speech2)
      })
    },
    options = list(height = 500)
)
```

### Topic Words

```{r warning=FALSE}
entertainment = read.csv("./data/topic_dict/entertainment-dict.csv", header = FALSE); entertainment = as.character(entertainment$V1)
exercise = read.csv("./data/topic_dict/exercise-dict.csv", header = FALSE); exercise = as.character(exercise$V1)
family = read.csv("./data/topic_dict/family-dict.csv", header = FALSE); family = as.character(family$V1)
food = read.csv("./data/topic_dict/food-dict.csv", header = FALSE); food = as.character(food$V1)
people = read.csv("./data/topic_dict/people-dict.csv", header = FALSE); people = as.character(people$V1)
pets = read.csv("./data/topic_dict/pets-dict.csv", header = FALSE); pets = as.character(pets$V1)
school = read.csv("./data/topic_dict/school-dict.csv", header = FALSE); school = as.character(school$V1)
shopping = read.csv("./data/topic_dict/shopping-dict.csv", header = FALSE); shopping = as.character(shopping$V1)
work = read.csv("./data/topic_dict/work-dict.csv", header = FALSE); work = as.character(work$V1)
```

```{r warning=FALSE}
topic_cnt = lapply(
  strsplit(data$sent, " "), function(x){
    c(sum(x %in% entertainment), sum(x %in% exercise),sum(x %in% family), sum(x %in% food),
      sum(x %in% people), sum(x %in% pets),sum(x %in% school), sum(x %in% shopping),sum(x %in% work))})
topic_cnt = as.data.frame(matrix(unlist(topic_cnt), ncol = 9, byrow = TRUE), 
                          col.names = c("entertainment", "exercise", "family", "food", "people",
                                        "pets", "school", "shopping", "work"))
data_topic = merge(data[, c("sent", "predicted_category")], topic_cnt, by.x = 0, by.y = 0)
temp = c("V1", "V2", "V3", "V4", "V5", "V6", "V7", "V8", "V9")
topic = data.frame(
  rbind(apply(data_topic[data_topic$predicted_category == "achievement", temp], 2, sum),
        apply(data_topic[data_topic$predicted_category == "affection", temp], 2, sum),
        apply(data_topic[data_topic$predicted_category == "bonding", temp], 2, sum),
        apply(data_topic[data_topic$predicted_category == "enjoy_the_moment", temp], 2, sum),
        apply(data_topic[data_topic$predicted_category == "exercise", temp], 2, sum),
        apply(data_topic[data_topic$predicted_category == "leisure", temp], 2, sum),
        apply(data_topic[data_topic$predicted_category == "nature", temp], 2, sum)), row.names = emtions)
colnames(topic) = c("entertainment", "exercise", "family", "food", "people", "pets", "school", "shopping", "work")

```

```{r warning=FALSE}
myhc_add_series_labels_values = function (hc, labels, values, text, colors = NULL, ...) 
{
    assertthat::assert_that(is.highchart(hc), is.numeric(values), 
        length(labels) == length(values))
    df <- dplyr::data_frame(name = labels, y = values, text=text)
    if (!is.null(colors)) {
        assert_that(length(labels) == length(colors))
        df <- mutate(df, color = colors)
    }
    ds <- list_parse(df)
    hc <- hc %>% hc_add_series(data = ds, ...)
    hc
}
```

## Using the files in topic-word folder, we can caculate how many different topics are used for different emotions. From the pie plot we can roughly find the relationship between emotions and topics, including work, entertainment, family and so on.

```{r warning=FALSE}
library(highcharter)
A = colnames(topic)
B = as.numeric(topic["achievement",])
C = as.numeric(topic["achievement",])
df = data.frame(A, B, C)

highchart() %>% 
  hc_chart(type = "pie", data=df) %>% 
  myhc_add_series_labels_values(labels=A, values=B, text=C) %>% 
  hc_tooltip(crosshairs=TRUE, borderWidth=5, sort=TRUE, shared=TRUE, table=TRUE,
     pointFormat=paste('<br><b>A: {point.percentage:.1f}%</b><br>C: {point.text}')) %>%
  hc_title(text="Pie Plot of Topic Words for Achievement", margin=20, style=list(color="#144746", useHTML=TRUE)) 
```

```{r warning=FALSE}
A = colnames(topic)
B = as.numeric(topic["affection",])
C = as.numeric(topic["affection",])
df = data.frame(A, B, C)

highchart() %>% 
  hc_chart(type = "pie", data = df) %>% 
  myhc_add_series_labels_values(labels=A, values=B, text=C) %>% 
  hc_tooltip(crosshairs=TRUE, borderWidth=5, sort=TRUE, shared=TRUE, table=TRUE,
     pointFormat=paste('<br><b>A: {point.percentage:.1f}%</b><br>C: {point.text}')) %>%
  hc_title(text="Pie Plot of Topic Words for Affection", margin=20, style=list(color="#144746", useHTML=TRUE)) 
```
